SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-04-17 results.tex
Paragraph spacing

The only benchmark where PPF fails to match the improvement offered by
other prefetchers is {\tt 607.cactuBSSN\_s}.  Based on our observation
of prefetching behavior, we gather that BOP's aggressive and localized
nature fits this workload very well; as opposed to SPPs lookahead
nature.  As a result, SPP, and hence PPF, underperform on this
benchmark.

@@

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC
of the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better
than the next best prefetcher -- SPP.

@@

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a
mix of multi-programmed workloads.

\noindent \textbf{4-Core:} Figure~\ref{Fig:4Core_SPEC2017}
shows a comparison of speedups obtained on 4-core mixes of a memory
intensive subset of SPEC CPU 2017. We plot all 4 prefetchers, normalized
to the baseline. The workloads have been sorted in increasing order of
the speedup. PPF offers a speedup of \textbf{51.2\%} on these traces,
an improvement of \textbf{11.4\%} over the underlying SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not
illustrated for space reasons), PPF provides an IPC speedup of
\textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.

\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}

\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.65\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the base engine SPP in a multi-core environment
is expected as PPF is a very accurate filter. Thus, it eliminates
useless prefetches before they can cause pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.

>>>>

The only benchmark where PPF fails to match the improvement offered by
any other prefetcher is {\tt 607.cactuBSSN\_s}. Based on our observation
of prefetching behavior, we gather that BOP's aggressive and localized
nature fits this workload very well; as opposed to SPPs lookahead
nature.  As a result, SPP, and hence PPF, underperform on this
benchmark.

@@

% djimenez: is this geometric mean? if so, say so.
% [EB] Resolved
On the full SPEC CPU 2017 suite, PPF improves the geometric mean IPC
of the baseline by \textbf{15.24\%}, which is \textbf{2.27\%} better
than the next best prefetcher -- SPP. {For PPF, the average 
lookahead depth over the full benchmark is 3.97, while it is 3.28 for just 
SPP. It is evident that on average for SPP, our scheme allows the 
prefetcher to speculate 21\% deeper.}

@@

\subsection{Multi-core Results}
\label{Results-Multi}
\noindent In this section, we demonstrate the improvement achieved by PPF for a
mix of multi-programmed workloads.
\newline
\newline
\noindent \textbf{4-Core:} Figure~\ref{Fig:4Core_SPEC2017}
shows a comparison of speedups obtained on 4-core mixes of a memory
intensive subset of SPEC CPU 2017. We plot all 4 prefetchers, normalized
to the baseline. The workloads have been sorted in increasing order of
the speedup. PPF offers a speedup of \textbf{51.2\%} on these traces,
an improvement of \textbf{11.4\%} over the underlying SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not
illustrated for space reasons), PPF provides an IPC speedup of
\textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.
%
\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}
%
\newline
\newline
\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.65\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the {underlying prefetcher, SPP,} 
in a multi-core environment is expected as PPF is a very accurate filter. 
Thus, it eliminates useless prefetches before they can cause pollution in the 
shared LLC. BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.
